---
title: "all"
author: "Asantewaa"
date: "`r Sys.Date()`"
output: html_document
---

## Introduction

This document looks at the performance of parametric estimators vs semi-parametric estimators with different initial estimators on confounded data across various sample sizes, focusing on their bias, variance, estimation accuracy, coverage, and confidence interval width of the average causal effect of treatment $T$ on outcome $Y$.

## Simulation Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(knitr)
library(broom)
library(MASS)  
library(survey)
library(tmle)
set.seed(123)  
```

## Data Generation

The following data is generated, representing scenarios that are both confounded and unconfounded:

-   Covariate $W$: $W \sim N(0,1)$.
-   Treatment $T$:
    -   Confounded: $T$ depends on $W$, modeled by $\text{Prob}(T = 1 | W) = \frac{1}{1 + e^{-(0.3 - 0.5 \cdot W)}}$.
    -   Unconfounded: $T$ is independent of $W$, with a fixed probability $\text{Prob}(T = 1) = \frac{1}{1 + e^{-0.3}}$ or $0.5$ since the common fair choice is a 50/50 chance of getting either treatment
-   Outcome $Y$: $Y \sim \mathcal{N} (e^{a + b\cdot T +c\cdot W + d\cdot W \cdot T},1)$.

```{r}
a <- 1
b <- -10
c <- 1
d <- 1

sample_sizes <- c(100, 500, 1000, 5000, 10000, 50000, 100000, 500000)
```

### 1. Objective Understanding

-   $a$ (Intercept): Adjusting $a$ shifts the baseline level of $Y$ for all observations when $T=0$ and $W=0$.
-   $b$ (Treatment effect): $b$ directly influences the impact of the treatment $T$ on $Y$. A higher absolute value of $b$ increases the treatment effect magnitude.
-   $c$ (Covariate effect): $c$ modifies how the covariate $W$ affects $Y$. Altering $c$ helps analyze how sensitivity to $W$ changes the outcome.
-   $d$ (Interaction effect): $d$ represents the interaction between $T$ and $W$, helping to evaluate whether the effect of $T$ on $Y$ changes with different levels of $W$.

### Confounded Data

```{r}
generate_confounded_data <- function(n) {
  W <- rnorm(n)
  T <- rbinom(n, 1, prob = 1 / (1 + exp(-0.3 + 0.5 * W)))
  Y <- rnorm(n, mean = exp(a + b*T +c*W + d*W*T), sd = 1)
  data.frame(W = W, T = T, Y = Y)
}
```

```{r}
n <- 100000  
data <- generate_confounded_data(n)
```

### DM Estimator and Confidence Intervals

```{r}
estimate_dm <- function(data) {
  treated <- data[data$T == 1, "Y"]
  control <- data[data$T == 0, "Y"]
  est <- mean(treated) - mean(control)
  se <- sqrt(var(treated) / length(treated) + var(control) / length(control))
  ci <- c(est - 1.96 * se, est + 1.96 * se)
  list(estimate = est, se = se, ci_lower = ci[1], ci_upper = ci[2])
}
```

### OLS Estimator and Confidence Intervals

```{r}
estimate_ols <- function(data) {
  model <- lm(Y ~ T + W + T*W, data = data)
  coef_est <- coef(summary(model))["T", ]
  ci <- confint(model, "T", level = 0.95)
  list(estimate = coef_est["Estimate"], se = coef_est["Std. Error"], ci_lower = ci[1], ci_upper = ci[2])
}
```

### IPW Estimator and Confidence Intervals

```{r}
estimate_ipw <- function(data) {
  
  propensity_model <- glm(T ~ W, family = binomial(link = "logit"), data = data)
  
  data$weights <- ifelse(data$T == 1, 
                         1 / predict(propensity_model, type = "response", newdata = data),
                         1 / (1 - predict(propensity_model, type = "response", newdata = data)))
  
  ipw_design <- svydesign(ids = ~1, weights = ~weights, data = data)
  
  ipw_result <- svyglm(Y ~ T, design = ipw_design)
  
  coef_ipw <- coef(ipw_result)
  se_ipw <- sqrt(diag(vcov(ipw_result)))
  
  ci_ipw <- coef_ipw["T"] + c(-1.96, 1.96) * se_ipw["T"]
  list(estimate = coef_ipw["T"], 
       se = se_ipw["T"], 
       ci_lower = ci_ipw[1], 
       ci_upper = ci_ipw[2])
}
```

The Problematic IPW

```{r}
estimate_ipw_ <- function(data) {
  
  count_table <-  table(data$T)
  
  data$weights <- ifelse(data$T == 1,count_table["1"]/nrow(data),
                        count_table["0"]/nrow(data) )
  
  ipw_design <- svydesign(ids = ~1, weights = ~weights, data = data)
  
  ipw_result <- svyglm(Y ~ T, design = ipw_design)
  
  coef_ipw <- coef(ipw_result)
  se_ipw <- sqrt(diag(vcov(ipw_result)))
  
  ci_ipw <- coef_ipw["T"] + c(-1.96, 1.96) * se_ipw["T"]
  list(estimate = coef_ipw["T"], 
       se = se_ipw["T"], 
       ci_lower = ci_ipw[1], 
       ci_upper = ci_ipw[2])
}

```

### OSE Estimator and Confidence Intervals

```{r}
estimate_ose <- function(data) {
  
  lm_model <- lm(Y ~ T + W + T*W, data = data)
  data$Q0W <- predict(lm_model, newdata = data.frame(T = 0, W = data$W))
  data$Q1W <- predict(lm_model, newdata = data.frame(T = 1, W = data$W))
  
  g_init <- glm(T ~ W, family = binomial, data = data)
  data$g1W <- predict(g_init, type = "response")
  data$g0W <- 1 - data$g1W
  
  data$H1 <- data$T / data$g1W
  data$H0 <- (1 - data$T) / data$g0W
  
  data$IF <- (data$H1 - data$H0) * (data$Y - (data$T * data$Q1W + (1 - data$T) * data$Q0W)) + (data$Q1W - data$Q0W)
  
  ATE <- mean(data$IF)
  SE <- sd(data$IF) / sqrt(nrow(data))
  CI_lower <- ATE - 1.96 * SE
  CI_upper <- ATE + 1.96 * SE
  
  return(list(estimate = ATE, se = SE, ci_lower = CI_lower, ci_upper = CI_upper))
}

```

### TMLE Estimator and Confidence Interval

```{r}
estimate_tmle <- function(data) {
  Q_init <- lm(Y ~ T + W + T * W, data = data)

  data$Q0W <- predict(Q_init, newdata = data.frame(T = 0, W = data$W))
  data$Q1W <- predict(Q_init, newdata = data.frame(T = 1, W = data$W))
  
  g_init <- glm(T ~ W, family = binomial, data = data)
  data$g1W <- predict(g_init, type = "response")
  data$g0W <- 1 - data$g1W

  data$H1 <- data$T / data$g1W
  data$H0 <- (1 - data$T) / data$g0W

  second_stage <- lm(Y ~ -1 + H1 + H0, offset = T*data$Q1W + (1-T)*data$Q0W, data = data, weights = rep(1, nrow(data)))
  epsilon <- coef(second_stage)

  data$Q0W_star <- data$Q0W + epsilon["H0"] * (1 - data$T) / data$g0W
  data$Q1W_star <- data$Q1W + epsilon["H1"] * data$T / data$g1W

  data$IF <- (data$H1 - data$H0) * (data$Y - (data$T * data$Q1W_star + (1 - data$T) * data$Q0W_star)) + (data$Q1W_star - data$Q0W_star)
  
  ATE <- mean(data$Q1W_star - data$Q0W_star)
  SE <- sd(data$IF) / sqrt(nrow(data))
  CI_lower <- ATE - 1.96 * SE
  CI_upper <- ATE + 1.96 * SE
  
  return(list(estimate = ATE, se = SE, ci_lower = CI_lower, ci_upper = CI_upper))
}

estimate_tmle(data)
```

```{r}
estimate_wtmle <- function(data) {
  Q_init <- lm(Y ~ T + W + T * W, data = data)

  data$Q0W <- predict(Q_init, newdata = data.frame(T = 0, W = data$W))
  data$Q1W <- predict(Q_init, newdata = data.frame(T = 1, W = data$W))
  
  g_init <- glm(T ~ W, family = binomial, data = data)
  data$g1W <- predict(g_init, type = "response")
  data$g0W <- 1 - data$g1W

  data$H1 <- data$T
  data$H0 <- (data$T - 1) 
  
  data$GW <- data$T / data$g1W + (1 - data$T) / data$g0W

  second_stage <- lm(Y ~ -1 + H1 + H0, offset = T*data$Q1W + (1-T)*data$Q0W, data = data, weights = data$GW )
  epsilon <- coef(second_stage)

  data$Q0W_star <- data$Q0W + epsilon["H0"] * (data$T - 1) 
  data$Q1W_star <- data$Q1W + epsilon["H1"] * data$T 

  data$IF <- (data$H1 + data$H0) * (data$Y - (data$T * data$Q1W_star + (1 - data$T) * data$Q0W_star)) + (data$Q1W_star - data$Q0W_star)
  
  ATE <- mean(data$Q1W_star - data$Q0W_star)
  SE <- sd(data$IF) / sqrt(nrow(data))
  CI_lower <- ATE - 1.96 * SE
  CI_upper <- ATE + 1.96 * SE
  
  return(list(estimate = ATE, se = SE, ci_lower = CI_lower, ci_upper = CI_upper))
}

estimate_wtmle(data)
```

## True Causal Effect

```{r}
true_effect <- exp(a+b+((c+d)^2)/2) - exp(a+(c^2)/2)
true_effect
```

### Simulation

```{r}
compare_estimators_ <- function(sample_sizes, num_sim = 200, scenario = "confounded") {
  results_list <- vector("list", length(sample_sizes))
  names(results_list) <- as.character(sample_sizes)
  
  for (size_index in seq_along(sample_sizes)) {
    n <- sample_sizes[size_index]
    dm_estimates <- numeric(num_sim)
    ols_estimates <- numeric(num_sim)
    ipw_estimates <- numeric(num_sim)
    ose_estimates <- numeric(num_sim)
    tmle_estimates <- numeric(num_sim)
    dm_coverage <- numeric(num_sim)
    ols_coverage <- numeric(num_sim)
    ipw_coverage <- numeric(num_sim)
    ose_coverage <- numeric(num_sim)
    tmle_coverage <- numeric(num_sim)
    dm_ci_widths <- numeric(num_sim)
    ols_ci_widths <- numeric(num_sim)
    ipw_ci_widths <- numeric(num_sim)
    ose_ci_widths <- numeric(num_sim)
    tmle_ci_widths <- numeric(num_sim)
    
    dm_variances <- numeric(num_sim)
    ols_variances <- numeric(num_sim)
    ipw_variances <- numeric(num_sim)
    ose_variances <- numeric(num_sim)
    tmle_variances <- numeric(num_sim)
    
    for (i in 1:num_sim) {
      if (scenario == "confounded") {
        data <- generate_confounded_data(n)
      } else {
        data <- generate_unconfounded_data(n)
      }
      
      dm_results <- estimate_dm(data)
      ols_results <- estimate_ols(data)
      ipw_results <- estimate_ipw_(data)
      ose_results <- estimate_ose(data)
      tmle_results <- estimate_tmle(data)
      
      dm_estimates[i] <- dm_results$estimate
      ols_estimates[i] <- ols_results$estimate
      ipw_estimates[i] <- ipw_results$estimate
      ose_estimates[i] <- ose_results$estimate
      tmle_estimates[i] <- tmle_results$estimate
      
      dm_coverage[i] <- (true_effect >= dm_results$ci_lower) & (true_effect <= dm_results$ci_upper)
      ols_coverage[i] <- (true_effect >= ols_results$ci_lower) & (true_effect <= ols_results$ci_upper)
      ipw_coverage[i] <- (true_effect >= ipw_results$ci_lower) & (true_effect <= ipw_results$ci_upper)
      ose_coverage[i] <- (true_effect >= ose_results$ci_lower) & (true_effect <= ose_results$ci_upper)
      tmle_coverage[i] <- (true_effect >= tmle_results$ci_lower) & (true_effect <= tmle_results$ci_upper)
      
      dm_ci_widths[i] <- dm_results$ci_upper - dm_results$ci_lower
      ols_ci_widths[i] <- ols_results$ci_upper - ols_results$ci_lower
      ipw_ci_widths[i] <- ipw_results$ci_upper - ipw_results$ci_lower
      ose_ci_widths[i] <- ose_results$ci_upper - ose_results$ci_lower
      tmle_ci_widths[i] <- tmle_results$ci_upper - tmle_results$ci_lower
      
      if (i > 1) {
        dm_variances[i] <- var(dm_estimates[1:i])
        ols_variances[i] <- var(ols_estimates[1:i])
        ipw_variances[i] <- var(ipw_estimates[1:i])
        ose_variances[i] <- var(ose_estimates[1:i])
        tmle_variances[i] <- var(tmle_estimates[1:i])
      }
    }
    
    dm_variance <- mean(dm_variances[2:num_sim]) 
    ols_variance <- mean(ols_variances[2:num_sim])
    ipw_variance <- mean(ipw_variances[2:num_sim])
    ose_variance <- mean(ose_variances[2:num_sim])
    tmle_variance <- mean(tmle_variances[2:num_sim])
    
    dm_rmse <- sqrt(mean((dm_estimates - true_effect)^2))
    ols_rmse <- sqrt(mean((ols_estimates - true_effect)^2))
    ipw_rmse <- sqrt(mean((ipw_estimates - true_effect)^2))
    ose_rmse <- sqrt(mean((ose_estimates - true_effect)^2))
    tmle_rmse <- sqrt(mean((tmle_estimates - true_effect)^2))
    
    results_list[[size_index]] <- data.frame(
      Sample_Size = rep(n, 5),
      Estimator = rep(c("DM", "OLS", "IPW", "OSE", "TMLE"), each = num_sim),
      Estimate = c(dm_estimates, ols_estimates, ipw_estimates, ose_estimates, tmle_estimates),
      Variance = c(rep(dm_variance, num_sim), rep(ols_variance, num_sim), rep(ipw_variance, num_sim), rep(ose_variance, num_sim), rep(tmle_variance, num_sim)),
      
      RMSE = c(rep(dm_rmse, num_sim), rep(ols_rmse, num_sim), rep(ipw_rmse, num_sim), rep(ose_rmse, num_sim), rep(tmle_rmse, num_sim)),
      Coverage = c(dm_coverage, ols_coverage, ipw_coverage, ose_coverage, tmle_coverage),
      CI_Width = c(dm_ci_widths, ols_ci_widths, ipw_ci_widths, ose_ci_widths, tmle_ci_widths)
    )
  }
  
  results_df <- do.call(rbind, results_list)
  return(results_df)
}

results_df_conf_ <- compare_estimators_(sample_sizes, num_sim = 200, scenario = "confounded")

```

## Simulations and Plots

```{r}
summary_df_conf <- results_df_conf_ %>%
  group_by(Sample_Size, Estimator) %>%
  summarize(
    Mean_Estimate = mean(Estimate),
    Bias = mean(Estimate - true_effect),
    Variance = mean(Variance),
    Bias.to.se = Bias/sqrt(Variance),
    RMSE = mean(RMSE),
    Coverage = mean(Coverage),
    Mean_CI_Width = mean(CI_Width),
    .groups = 'drop'
  )

kable(summary_df_conf, caption = "Performance Metrics for DM ,IPW ,OLS, OSE and TMLE Estimators Across Different Sample Sizes")
```

```{r}
# Select dataset
summary_df <- summary_df_conf

# Bias Plot
ggplot(summary_df, aes(x = log10(Sample_Size), y = Bias, color = Estimator)) +
  geom_line() +
  geom_point() +
  labs(title = "Bias Across Sample Sizes", x = "Log of Sample Size", y = "Bias")

# Variance Plot
ggplot(summary_df, aes(x = log10(Sample_Size), y = Variance, color = Estimator)) +
  geom_line() +
  geom_point() +
  labs(title = "Variance Across Sample Sizes", x = "Log of Sample Size", y = "Variance")

# Bias.to.se Plot
ggplot(summary_df, aes(x = log10(Sample_Size), y = Bias.to.se, color = Estimator)) +
  geom_line() +
  geom_point() +
  labs(title = "Bias-to-se Ratio Across Sample Sizes", x = "Log of Sample Size", y = "Bias.to.se")

# RMSE Plot
ggplot(summary_df, aes(x = log10(Sample_Size), y = RMSE, color = Estimator)) +
  geom_line() +
  geom_point() +
  labs(title = "RMSE Across Sample Sizes", x = "Sample Size", y = "RMSE")

# Coverage Plot
ggplot(summary_df, aes(x = log10(Sample_Size), y = Coverage, color = Estimator)) +
  geom_line() +
  geom_point() +
  labs(title = "Coverage Probability Across Sample Sizes", x = "Log of Sample Size", y = "Coverage")

# Confidence Interval Width Plot
ggplot(summary_df, aes(x = log10(Sample_Size), y = Mean_CI_Width, color = Estimator)) +
  geom_line() +
  geom_point() +
  labs(title = "Confidence Interval Width Across Sample Sizes", x = "Log of Sample Size", y = "CI Width")
```
